---
title: "Getting Started"
author: "Nate Vogel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```


`LegalServerReader` provides a few simple functions for accessing the LegalServer Reports API and storing credentials for the api in a way that is at least somewhat more secure than storing the credentials in plain text files in your project directory. 

`LegalServerReader` uses your system's GPG (GNU Privacy Guard) to encrypt and then decrypt credentials for your LegalServer API reports. It then can download the report and provide it to you as a dataframe. You can also use this library to map LegalServer's internal column names from things like "built_in_matter_colname_colname" to more helpful names like "Case ID Number".


# Getting Started using LegalServerReader

## Generate a password-protected GPG key

You'll be using the GNU Privacy Guard tool to encrypt and decrpyt credentials. See (https://help.github.com/articles/generating-a-new-gpg-key/)[here] for instructions on generating a key. Make sure you use a good passphrase for securing the key itself.

## Save Credendtials for a report. 

Load the library, and then use it to save and encrypt credentials to a LegalServer report.

To save credentials, call the function `create.credentials`. This function will ask you for the username and password of the api user account from LegalServer.

```{r}
  creds <- create.credentials()
```

Next, add reports to this set of credentials.

```{r}
  creds <- add.report("First Report")
  creds <- add.report("Next Report")
```

`add.report` will prompt you to enter the url of the report. The url should include the api key that LegalServer generates for the report.

The name of the report you create here is just a friendly name for organizing credentials. It does not need to be related at all to what the LegalServer name of the report is.

Finally, save the credentials to an encrypted file, using your gpg key.

```{r} 
  save.credentials(creds, receiver = "mykey@test.com",
                   path.for.secrets =  "path/to/file.gpg")
```

This function requires you to identify the gpg key you will use for encryption, using the parameter `receiver`. This can be the ID of the key, or the email address of the key.

You can also include the `path.for.secrets`, which should be the path, including the filename, of the file where credentials should be saved. The file should end with the extension `.gpg`. By default, `save.credentials` will save the file in your working directory as `credentials.gpg`.

Finally, another optional parameter is `return.creds`. By default this is `FALSE`, but if you set it to true, `save.credentials` will return a `list` object with your saved credentials. You will pass this list to the `get.report` function to download a report from LegalServer.

You can use pipes to create and save credentials as in:

```{r}
creds <- create.credentials() %>%
         add.report("First Report") %>%
         add.report("Second Report") %>%
         save.credentials(receiver="mykey@test.com", 
                          path.for.secrets="./secrets.gpg", 
                          return.creds = TRUE)
```

## Load saved credentials

After you have saved credentials to a file, you can unencrypt them and load them into R as a list using `get.credentials`. The GPG application will be able to tell from the encrypted file which key was used to encrypt it, so you do not need to identify the key. You should identify the `credentials.path`, if it is anything other than the default "./credentials.gpg".

```{r}
creds <- get.credentials(credentials.path = "./credentials.gpg")
```

## Download a report.

To download a report using your credentials, use `get.report`. This function needs two parameters. First, `credentials` is a list of api credentials in the format created by `save.credentials`. `report.name` is the name you created in the credentials for your report. 

```{r}
rpt <- get.report(credentials = creds, report.name = "My Report from LegalServer")
```

## Renaming Columns

LegalServer reports download with names that reflect internal LegalServer structure, but are not as helpful in our context, like "builtin_matter_id_matter_id". So `LegalServerReader` provides a mechanism for configuring a mapping from LegalServer's column names to friendlier column names. 

First, you'll create an a configuration file in the `.ini` format. It will have a section that starts with your report name (the same name you used in `credentials.gpg`). And in that section will be a list of `key=value` pairs mapping LegalServer's column names to your preferred names. For example:

    [My Report]
    unhelpful_internal_colname_1=Case ID
    other_long_internal_colname=Client Age
    
Next, you'll load this mapping and use it to rename the columns of your report.

```{r}
mapper <- get.column.mapper(config.file="~/path/to/mapper.ini")
rpt.renamed <- remap.columns(rpt, mapper)
```

That's it!
