---
title: "Getting Started"
author: "Nate Vogel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=FALSE
)
```


`LegalServerReader` provides a few simple functions for accessing the LegalServer Reports API and storing credentials for the api in a way that is at least somewhat more secure than storing the credentials in plain text files in your project directory. 

`LegalServerReader` uses an encryption library called Sodium to encrypt and then decrypt credentials for your LegalServer API reports. It then can download the report and provide it to you as a dataframe. You can also use this library to map LegalServer's internal column names from things like "built_in_matter_colname_colname" to more helpful names like "Case ID Number".


# Getting Started using LegalServerReader


## Create Credendtials for a report. 

Load the library, and then use it to save and encrypt credentials to a LegalServer report.

The library supports both types of Legal Server reports api credentials. Basic Auth credentials have a username and a password. Bearer Token credentials have a secret token.

To create credentials, call the function `create.bearer.credentials` or `create.basic.auth.credentials`. This function will ask you for the username and password of the api user account from LegalServer, or the secret authentication token.

Next, add reports to this set of credentials.

```{r}
  creds <- add.report("First Report")
  creds <- add.report("Next Report")
```

`add.report` will prompt you to enter the url of the report. The url should include the api key that LegalServer generates for the report.

The name of the report you create here is just a friendly name for organizing credentials. It does not need to be related at all to what the LegalServer name of the report is.

## Save Credentials to a file

This library uses `sodium` to symmetrically encrypt your credentials.

```{r}
  creds <- create.credentials()
```

Finally, save the credentials to an encrypted file. `save.credentials` will ask you for a password for encryption.

```{r} 
  save.credentials(creds, path.for.secrets =  "path/to/secret.creds")
```

The `path.for.secrets` is the path to the encrypted credentials file. 

Finally, another optional parameter is `return.creds`. By default this is `FALSE`, but if you set it to true, `save.credentials` will return a `list` object with your saved credentials. You will pass this list to the `get.report` function to download a report from LegalServer.

You can use pipes to create and save credentials as in:

```{r}
creds <- create.credentials() %>%
         add.report("First Report") %>%
         add.report("Second Report") %>%
         save.credentials(path.for.secrets="~/secret.creds", 
                          return.creds = TRUE)
```

## Load saved credentials

After you have saved credentials to a file, you can unencrypt them and load them into R as a list using `get.credentials`. You should identify the `credentials.path`.

```{r}
creds <- get.credentials(credentials.path = "~/secret.creds")
```

## Download a report.

To download a report using your credentials, use `get.report`. This function needs two parameters. First, `credentials` is a list of api credentials in the format created by `save.credentials`. `report.name` is the name you created in the credentials for your report. 

```{r}
rpt <- get.report(credentials = creds, report.name = "My Report from LegalServer")
```

## Renaming Columns

If you'd like to rename the columns that get downloaded from LegalServer, `LegalServerReader` provides a mechanism for configuring a mapping from LegalServer's column names to friendlier column names. 

First, you'll create an a configuration file in the `.ini` format. It will have a section that starts with your report name (the same name you used in `credentials.gpg`). And in that section will be a list of `key=value` pairs mapping LegalServer's column names to your preferred names. For example:

    [My Report]
    unhelpful_internal_colname_1=Case ID
    other_long_internal_colname=Client Age
    
Next, you'll load this mapping and use it to rename the columns of your report.

```{r}
mapper <- get.column.mapper(config.file="~/path/to/mapper.ini")
rpt.renamed <- remap.columns(rpt, mapper)
```

That's it!
